Items

### 2021-08-25 proposal.Rmd
- saved

  Competing Interests: Both authors declare no competing interests.

  Data Accessibility Statement: All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/7ncpk/).

  Funding Information: During the conception and data collection of the prestudy, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported a research stay at UCSB. During some time working on the article and while at University of Hohenheim, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy". TD is now funded by a regular and not-tenured assistant professorship at University of Vienna. MM is funded by a regular and tenured full professorship at UCSB.

# Author contribution: conception and design: TD, MM; acquisition of data: MM, TD; code: TD; analysis and interpretation of data: TD, MM; First draft: TD; Revisions & Comments: TD & MM

@@

To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018], which is in the tradition of Big Five approach [@johnBigFiveTrait1999] and which represents a broad understanding of personality.
The HEXACO inventory measures overall six factors (see below), which each have four more specific facets. 
Including the facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations with the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and include also specific personality facets.
Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility plus a facet labeled Altruism, which seem promising to investigate the nothing to hide argument. 
We chose 
<!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
In what follows, we briefly present all factors and outline how they and selected facets might relate to privacy.

@@

>>>>

@@

To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
The HEXACO model is in the tradition of Big Five approach [@johnBigFiveTrait1999], and it represents a broad understanding of personality.
It measures overall six factors (see below), which have four specific facets each. 
Building not only on factors but also facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and include also specific personality facets.
Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility, plus a facet labeled Altruism, which together seem promising to investigate the nothing to hide argument. 
<!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
In what follows, we briefly present all factors and outline how they and selected facets might relate to privacy.

@@

# Contributions

Conception and design: TD, MM. Data acquisition: TD. Code: TD. Analysis and interpretation of data: TD, MM; First draft: TD; Revisions & Comments: TD & MM.

# Funding Information

During the conception and data collection of the prestudy, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported a research stay at UCSB. During some time working on the article and while at University of Hohenheim, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy". TD is now funded by a regular and not-tenured assistant professorship at University of Vienna. MM is funded by a regular and tenured full professorship at UCSB.

# Competing Interests

Both authors declare no competing interests.

# Supplementary Material

All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/7ncpk/). The paper also has a companion website where all materials can be accessed ().

# Data Accessibility Statement

The data will be shared on the open science framework (https://osf.io/7ncpk/).
